\vspace{-0.25em}\thetitle

### 2009-07-24 paper.tex
...

This paper is the first in a three-part series, employing non-parametric discrete mixture modeling to understand and analyze network traffic patterns at the level of individual flows and packets.\flownote
All three papers employ the same theoretical framework but investigate different fundamental applications of traffic modeling:
prediction, classification and generation.
In this paper we first present the framework and then demonstrate how it can predict detailed behavior of individual flows from the observation of only a handful of initial packets.
% The following papers will focus on classification of flows according to application type and realistic workload generation.

>>>>

This paper is the first in a three-part series employing a numerical linear algebra techniques to understand and analyze network traffic patterns at a detailed level of individual flows and packets.\flownote
All three papers employ the same theoretical framework but investigate different fundamental applications of traffic modeling:
prediction, classification and generation.
In this paper we first present the framework and then demonstrate how it can predict the behavior of individual flows from the observation of only a handful of their initial packets.
% The following papers will focus on classification of flows according to application type and realistic workload generation.
